Determining multi-scale controls on river temperature: a time series approach

### 2017-04-07 manuscript/manuscript.tex
changed SDC citation

Temperature buffering by snow and ice appears to be enhanced by the action of artificial impoundments. Eight sites on five rivers included in this study are (or were until 2014, in the case of the Elwha River) interrupted by dams or embankments that release stored water from the bases of their reservoirs. At 33 m, even the shallowest of these reservoirs is deep enough to stratify in summer, meaning released water would be delivered from the cold hypolimnion \citep{olden_hypoCold}. This certainly would have affected temperature readings for the Green, Elwha, Cedar and upper Skagit River sites, whose mainstems are or were dammed upstream of the sample location. The impact of damming on temperature readings at the Skokomish and the lower Skagit River sites should be lesser, as major, unobstructed river forks intercede between sample location and dam, resetting or partially resetting natural conditions \citep{ward1983serial}. These sites are RS and SD, respectively, and both fall almost exactly on the regression line in Figure 4a. The upper Skagit site therefore occupies a middling space of $\textrm{T}_{air}\rightarrow \textrm{T}_{water}$ coupling between ``fully'' obstructed and unobstructed SD sites.

>>>>

Temperature buffering by snow and ice appears to be enhanced by the action of artificial impoundments. Eight sites on five rivers included in this study are (or were until 2014, in the case of the Elwha River) interrupted by dams or embankments that release stored water from the bases of their reservoirs. At 33 m, even the shallowest of these reservoirs is deep enough to stratify in summer, meaning released water would be delivered from the cold hypolimnion \citep{olden_hypoCold}. This certainly would have affected temperature readings for the Green, Elwha, Cedar and upper Skagit River sites, whose mainstems are or were dammed upstream of the sample location. The impact of damming on temperature readings at the Skokomish and the lower Skagit River sites should be lesser, as major, unobstructed river forks intercede between sample location and dam, resetting or partially resetting natural conditions \citep{stanford2001revisiting}. These sites are RS and SD, respectively, and both fall almost exactly on the regression line in Figure 4a. The upper Skagit site therefore occupies a middling space of $\textrm{T}_{air}\rightarrow \textrm{T}_{water}$ coupling between ``fully'' obstructed and unobstructed SD sites.
